Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-29 paper/main_RA-L_v1_nadia.tex
Added demo videos link for further reference
Latest updates on Section 5 in _nadia.tex

\clearpage
\section{Experimental Validation} \label{Sec:Exp}
%\textcolor{red}{We should try to have page 5 start with this section, i.e. we must reduce 1 full column from the previous sections.}
\subsection{JT-DS Learning Performance  Evaluation}
To evaluate the proposed JT-DS learning algorithm we collected kinesthetic demonstrations on a 7-DOF KUKA LWR 4+ robot arm, for 6 different tasks (see Table \ref{tab:learning}) which require mimicking the demonstrated joint-space behavior while reaching for a single target in task space. These behaviors include (as shown in Fig. \ref{fig:behaviors} ):
\begin{itemize}[leftmargin=*]
\item \textit{(1-2) Tennis strokes:} For these particular behaviors, we guide the robot to perform a forehand and backhand stroke.  
\item \textit{(3-4) Pouring motions:} We guide the robot to pour chips on a bowl. The first instance is without an obstacle in the workspace, which is demonstrated as a linear joint interpolation. The second instance is with an obstacle, where the human is seen folding the elbow and lowering the shoulder of the robot arm to avoid the obstacle. 
\item \textit{(5) Footstep-like motion:} We demonstrate a footstep motion which begins with a straight leg, moving through a singularity, and finally bringing the knee up.
\item \textit{(6) Singularity motions:} For this behavior we simulate joint trajectories in which the base rotates and all of the other joints are locked in a singular configuration.
\end{itemize}

For each behavior, we collected $M$ demonstrations consisting of ($14$-D) time-series $\boldsymbol{\xi}^{(i)} = \{\xi_1^{(i)},\dots,\xi_T^{(i)}\}$ for $i= \{1,\dots,M\}$. The $14$ dimensions in $\xi_t = [q_t,\dot{q_t}]^T$ correspond to joints angles and velocities. We also record the final task-space configurations ${x^*}^{(i)}$, which we assume is the attractor in task-space. The recordings are initially collected at a rate of 500 Hz. However, our learning approach does not require such a dense representation of the trajectories, hence we down-sample them to 25 Hz. The total number of demonstrations $M$ and samples per \textit{behavior dataset} $M^*T$ are provided in Table \ref{tab:learning}. Given these datasets, we seek to: 
\begin{enumerate}[leftmargin=*]
\item Verify that the learned \textit{behavior synergies} are capable of generating the desired joint-space behaviors.  
\item Find the dimensionality approach which yields the best trade-off between accuracy and model complexity; i.e. the least dimensions $\delta$ and synergies $K$.
\end{enumerate}
We thus evaluate three learning approaches with different dimensionality reduction algorithms: (1) None, (2) PCA and (3) K-PCA with RBF kernel.
We perform 10-fold cross-validation on all datasets, for each learning approach, with a training/testing ratio of $60 \%$. To evaluate performance, we take the square root of the MSE defined in \eqref{eq:optim_error}, which we refer to as the joint-velocity RMSE.

Performing such cross-validation in our case, is however not straight-forward, as our $\mathcal{A}(q)$ formulation has several hyper-parameters, namely the dimensionality $\delta$ of our lower-dimensional embedding $\phi(q)$ and the number of local behavior synergies $K$. Moreover, when using K-PCA (with RBF kernel $k(q,q') = \exp(-\frac{||q-q'||^2}{2\sigma^2})$) we must also find the optimal width $\sigma$ in the RBF kernel. Thus, for each fold and each learning approach we find the optimal hyper-parameters $\delta$, $K$ and $\sigma$ (when applicable), as follows:
\textcolor{red}{\begin{enumerate}[leftmargin=*]
\item Explain how optimal $\delta$ is computed for PCA. 
\item Explain how optimal $\delta$ and $\sigma$ are found for K-PCA.
\item Explain how optimal $K$ is computed for GMM.
\end{enumerate}}

\begin{figure}[t]
	\centering	
		\begin{subfigure}[t]{\linewidth}
		\centering
			\includegraphics[width=0.5\linewidth]{new-pics/forehand_crop.png}\hspace{5pt}\includegraphics[width=0.43\linewidth]{new-pics/backhand_crop.png}
					\caption{Tennis Strokes (left) Forehand (right) Backhand.}
		\end{subfigure}
		\begin{subfigure}[t]{\linewidth}
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-free_crop.png}\hspace{5pt}\includegraphics[width=0.477\linewidth]{new-pics/pour-obst_crop.png}
						\caption{Pouring Motions (left) without obstacle (right) with obstacle.}
			\end{subfigure}
			\begin{subfigure}[t]{\linewidth}		
\centering
	\includegraphics[width=0.475\linewidth]{new-pics/footstep.png}\hspace{5pt}\includegraphics[width=0.4475\linewidth]{new-pics/singularity_crop.png}
	\caption{(left) Foot-step motion (right) Singularity motions.}
				\end{subfigure}
	\caption{Demonstrated Joint-Space Behaviors with Task-Space Targets. \label{fig:behaviors}}
	\vspace{-10pt}
\end{figure}

\begin{table*}[!t]
\scriptsize
\caption{\scriptsize Performance Comparison of Learning Approach with different Dimensionality Reduction Schemes. We present the \texttt{mean(std)} for the optimal lower-dimensional $d$ and behavior synergies $K$ and RMSE on training and testing set, found for every learning scheme over 10 runs.\label{tab:learning}}
\begin{center}
\begin{tabular}{cc|cc|cc}
    \hline
    \hline
    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
	\\  
    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline

@@

	\multicolumn{1}{c}{\multirow{3}{*}{Pouring - Free}} & None & 7 & \textbf{ 4.1 $\pm$ (1.286)} & 0.163 $\pm$ (0.026) & 7.609 $\pm$ (18.99) \\
   \multicolumn{1}{c}{\multirow{3}{*}{($M=9,M^*T=1032$)}} & PCA & \textbf{ 2.3 $\pm$ (0.483)} & 4.8 $\pm$ (2.044) & \textbf{ 0.161 $\pm$ (0.034) } & \cellcolor{blue!10} 0.623 $\pm$ (0.301) \\	
	& K-PCA ($\sigma = 3.92$) & 3 & 4.3 $\pm$ (1.767) & 0.171 $\pm$ (0.106) & \cellcolor{blue!15} 0.511 $\pm$ (0.305)   \\
				\hline
	\multicolumn{1}{c}{\multirow{3}{*}{Pouring - Obstacle}} & None & 7 & 6.2 $\pm$ (2.573) & \textbf{0.247 $\pm$ (0.039)} & 3.049 $\pm$ (3.113) \\
   \multicolumn{1}{c}{\multirow{3}{*}{($M=11,M^*T=1232$)}} & PCA & 3.8 $\pm$ (0.421) & 3.8 $\pm$ (1.549) & 0.292 $\pm$ (0.018) & \cellcolor{blue!10} 0.486 $\pm$ (0.125) \\	
				& K-PCA ($\sigma = 7.695$) & \textbf{ 3.1 $\pm$ (0.421) } & 3.1 $\pm$ (0.316) & 0.288 $\pm$ (0.020) & \cellcolor{blue!15} 0.482 $\pm$ (0.078)   \\
				\hline	
	\multicolumn{1}{c}{\multirow{3}{*}{Foot Swing}} & None & 7 & 4.4 $\pm$ (2.366) & \textbf{ 0.080 $\pm$ (0.008) } & 0.368 $\pm$ (0.265)  \\
	\multicolumn{1}{c}{\multirow{3}{*}{($M=8,M^*T=1058$)}} & PCA & \textbf{1} & 3.2 $\pm$ (0.421) & 0.084 $\pm$ (0.004) & \cellcolor{blue!10}  0.123 $\pm$ (0.011) \\	
	& K-PCA ($\sigma = 1.513$) & 3.2 $\pm$ (0.421) & \textbf{3} &  0.091 $\pm$ (0.007) & \cellcolor{blue!15} 0.115 $\pm$ (0.015)   \\
				\hline

	\multicolumn{1}{c}{\multirow{3}{*}{Singularity Motions}} & None & 7 & 6.2 $\pm$ (2.898) & 0.054 $\pm$ (0.009) & 0.137 $\pm$ (0.098)  \\
    \multicolumn{1}{c}{\multirow{3}{*}{($M=10,M^*T=1467$)}} & PCA & \textbf{2} & 6 $\pm$ (2.357) & \textbf{ 0.053 $\pm$ (0.010) } & \cellcolor{blue!10} 0.105 $\pm$ (0.046) \\	
	& K-PCA ($\sigma = 1.769$) & 3.6 $\pm$ (0.516) & \textbf{5.3 $\pm$ (2.452)} & 0.055 $\pm$ (0.018) & \cellcolor{blue!15} 0.071 $\pm$ (0.010)   \\ \hline\hline
\end{tabular}
\end{center}
\vspace{-10pt}

\end{table*}

@@

\begin{figure}[t]
\vspace{-0.05cm}
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=0.45\linewidth]{Pic/Luggage1.png}
		\includegraphics[width=0.143\linewidth]{Pic/Luggage2.png}
		\includegraphics[width=0.377\linewidth]{Pic/Luggage3.png}
		\caption{Desired Joint Behavior: obstacle avoidance motion. The luggage is the obstacle.}
		\label{fig:snapshot:a}
	\end{subfigure}\\
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=0.33\linewidth]{Pic/Luggage4_SEDS.png}
		\includegraphics[width=0.33\linewidth]{Pic/Luggage3_SEDS.png}
		\includegraphics[width=0.32\linewidth]{Pic/Luggage3_SEDS.png}
		\caption{Desired Behavior: The Cartesian DS is used to generate the motion.}
		\label{fig:snapshot:b}
	\end{subfigure}\\
	\begin{subfigure}[t]{\linewidth}
	\centering	
		\includegraphics[width=0.45\linewidth]{Pic/1.png}~~
		\includegraphics[width=0.45\linewidth]{Pic/3.png}\\\vspace{0.1cm}
		\includegraphics[width=0.45\linewidth]{Pic/4.png}~~
		\includegraphics[width=0.45\linewidth]{Pic/2.png}
		\caption{Desired Joint Behavior: Foot step-like motion.}
		\label{fig:snapshot:c}
	\end{subfigure}\\	
	\caption{Snapshots of the robot experiments. A corresponding video is available on-line \href{https://youtu.be/1dgKfmN1UgE}{https://youtu.be/1dgKfmN1UgE}.}
	\label{fig:snapshot}
	\vspace{-0.8cm}
\end{figure}

@@

@@

\begin{figure}[h]
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{Pic/cropped_Sing_1.pdf}
		\caption{ }
		\label{fig:Sin}
	\end{subfigure}\\
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{Pic/cropped_Sing_2.pdf}
		\caption{ }
		\label{fig:Det}
	\end{subfigure}\\
	\caption{The experiment generated $K=3$ Gaussian components. As the first joint is the only joint which was not fixed during the demonstration, the learned augmentation matrices had only one nonzero entry $A_k(1,1)\neq0~\forall k\in \{1, 2, 3\} $.  In (a), the end-effector positions for the demonstrations and executed motions are plotted in Cartesian space. The JT-DS trajectory was generated closed-loop, while the SEDS trajectory was generated open-loop (otherwise it would be unstable). In (b), the determinants of the Jacobian $(|J(q)J^T(q)|)$ for all $10$ JT-DS motions are superimposed. Due to sensory noise, the determinants are not exactly zero, but are very close.  }
	\vspace{-10pt}
\end{figure}

>>>>

\begin{figure*}[!ht]
  \begin{minipage}[b]{0.3\textwidth}
	\centering	
		\begin{subfigure}[t]{\linewidth}
		\centering
			\includegraphics[width=0.5\linewidth]{new-pics/forehand_crop.png}\hspace{5pt}\includegraphics[width=0.43\linewidth]{new-pics/backhand_crop.png}
					\caption{Tennis Strokes (1-2).}
		\end{subfigure}
		\begin{subfigure}[t]{\linewidth}
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-free_crop.png}\hspace{5pt}\includegraphics[width=0.477\linewidth]{new-pics/pour-obst_crop.png}
						\caption{ Pouring Motions (3-4)}
			\end{subfigure}
			\begin{subfigure}[t]{\linewidth}		
\centering
	\includegraphics[width=0.45\linewidth]{new-pics/pour-obst-2_crop.png}\hspace{5pt}\includegraphics[width=0.5\linewidth]{new-pics/footstep.png}
	\caption{ Pouring Motion (5) and Foot-step (6).}
				\end{subfigure}
    \captionof{figure}{Demonstrated Joint-Space Behaviors with Task-Space Targets. \href{https://www.dropbox.com/sh/3vx512oldgbnkq5/AABP5iEqO0oYn7dlE-gvK1kPa?dl=0}{[videos]} \label{fig:behaviors}}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.7\textwidth}
    \scriptsize
    \centering
\resizebox{\linewidth}{!}{\begin{tabular}{cc|cc|cc}
    \hline
    \hline
    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
	\\  
    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline

@@

	\multicolumn{1}{c}{\multirow{3}{*}{Pouring - Free}} & None & 7 & \textbf{ 4.1 $\pm$ (1.286)} & 0.163 $\pm$ (0.026) & 7.609 $\pm$ (18.99) \\
   \multicolumn{1}{c}{\multirow{3}{*}{($M=9,M^*T=1032$)}} & PCA & \textbf{ 2.3 $\pm$ (0.483)} & 4.8 $\pm$ (2.044) & \textbf{ 0.161 $\pm$ (0.034) } & \cellcolor{blue!10} 0.623 $\pm$ (0.301) \\	
	& K-PCA ($\sigma = 3.92$) & 3 & 4.3 $\pm$ (1.767) & 0.171 $\pm$ (0.106) & \cellcolor{blue!15} 0.511 $\pm$ (0.305)   \\
				\hline
	\multicolumn{1}{c}{\multirow{3}{*}{Pouring - Obstacle 1}} & None & 7 & 6.2 $\pm$ (2.573) & \textbf{0.247 $\pm$ (0.039)} & 3.049 $\pm$ (3.113) \\
   \multicolumn{1}{c}{\multirow{3}{*}{($M=11,M^*T=1232$)}} & PCA & 3.8 $\pm$ (0.421) & 3.8 $\pm$ (1.549) & 0.292 $\pm$ (0.018) & \cellcolor{blue!10} 0.486 $\pm$ (0.125) \\	
				& K-PCA ($\sigma = 7.695$) & \textbf{ 3.1 $\pm$ (0.421) } & 3.1 $\pm$ (0.316) & 0.288 $\pm$ (0.020) & \cellcolor{blue!15} 0.482 $\pm$ (0.078)   \\
				\hline

	\multicolumn{1}{c}{\multirow{3}{*}{\textcolor{red}{Pouring - Obstacle 2}}} & None & 7 & X $\pm$ (Y) & X $\pm$ (Y) & X $\pm$ (Y) \\
   \multicolumn{1}{c}{\multirow{3}{*}{($M=X,M^*T=Y$)}} & PCA & X $\pm$ (Y) & X $\pm$ (Y) & X $\pm$ (Y) & X $\pm$ (Y) \\	
				& K-PCA ($\sigma = X$) & X $\pm$ (Y) & X $\pm$ (Y) & X $\pm$ (Y) & X $\pm$ (Y)  \\
				\hline

	\multicolumn{1}{c}{\multirow{3}{*}{Foot Step}} & None & 7 & 4.4 $\pm$ (2.366) & \textbf{ 0.080 $\pm$ (0.008) } & 0.368 $\pm$ (0.265)  \\
	\multicolumn{1}{c}{\multirow{3}{*}{($M=8,M^*T=1058$)}} & PCA & \textbf{1} & 3.2 $\pm$ (0.421) & 0.084 $\pm$ (0.004) & \cellcolor{blue!10}  0.123 $\pm$ (0.011) \\	
	& K-PCA ($\sigma = 1.513$) & 3.2 $\pm$ (0.421) & \textbf{3} &  0.091 $\pm$ (0.007) & \cellcolor{blue!15} 0.115 $\pm$ (0.015)   \\
				\hline

	\multicolumn{1}{c}{\multirow{3}{*}{Singularity Motions}} & None & 7 & 6.2 $\pm$ (2.898) & 0.054 $\pm$ (0.009) & 0.137 $\pm$ (0.098)  \\
    \multicolumn{1}{c}{\multirow{3}{*}{($M=10,M^*T=1467$)}} & PCA & \textbf{2} & 6 $\pm$ (2.357) & \textbf{ 0.053 $\pm$ (0.010) } & \cellcolor{blue!10} 0.105 $\pm$ (0.046) \\	
	& K-PCA ($\sigma = 1.769$) & 3.6 $\pm$ (0.516) & \textbf{5.3 $\pm$ (2.452)} & 0.055 $\pm$ (0.018) & \cellcolor{blue!15} 0.071 $\pm$ (0.010)   \\ \hline\hline
\end{tabular}}
      \captionof{table}{\scriptsize Performance Comparison of Learning Approach with different Dim. Red. Schemes. We present the \texttt{mean(std)} for the optimal $\delta$, $K$ and joint-velocity RMSE on training and testing set, found for every learning scheme over 10 runs.\label{tab:learning}}
    \end{minipage}
\end{figure*}

\newpage
\section{Experimental Validation} \label{Sec:Exp}
\subsection{JT-DS Learning Performance  Evaluation}
To evaluate the proposed JT-DS learning algorithm we collected kinesthetic demonstrations on a 7-DOF KUKA LWR 4+ robot arm, for 7 different tasks (see Table \ref{tab:learning}) which require mimicking the demonstrated joint-space behavior while reaching for a single target in task space. These behaviors include (as shown in Fig. \ref{fig:behaviors} ):
\begin{itemize}[leftmargin=*]
\item \textit{(1-2) Tennis strokes:} For these particular behaviors, we guide the robot to perform a forehand and backhand stroke.  
\item \textit{(3-5) Pouring motions:} We guide the robot to pour chips in a bowl with three different joint-space behaviors. The first is without an obstacle in the workspace. The second is with an obstacle in the upper hemisphere of the workspace, where the human is seen folding the elbow and lowering the shoulder of the robot arm to avoid the obstacle. The third instance is with an obstacle in the lower hemisphere, and now the human raises the shoulder to avoid it.
\item \textit{(6) Footstep-like motion:} We demonstrate a footstep motion which begins with a straight leg, moving through a singularity, and finally bringing the knee up.
\item \textit{(7) Singularity motions:} For this behavior we simulate joint trajectories in which the base rotates and all of the other joints are locked in singular configurations.
\end{itemize}

\noindent For each behavior, we collected $N$ demonstrations consisting of ($14$-D) time-series $D=\{\{ q_{t,n},\dot{q}_{t,n} \}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$ where each demonstration has duration $T_n$. We also record the final task-space configurations ${x^*}^{(n)}$, which we assume is the attractor in task-space. The recordings are collected at a rate of 500 Hz. However, our learning approach does not require such a dense representation of the trajectories, hence we down-sample them to 25 Hz. The total number of demonstrations $N$ and samples per \textit{dataset} $M = \sum_{n=1}^{N}T_n$ are provided in Table \ref{tab:learning}. Given these datasets, we seek to: 
\begin{enumerate}[leftmargin=*]
\item Verify that the learned \textit{behavior synergies} are capable of generating the demonstrated joint-space behaviors.  
\item Find the dimensionality approach which yields the best trade-off between accuracy and model complexity; i.e. the least dimensions $\delta$ and synergies $K$.
\end{enumerate}
We thus evaluate three learning approaches with different dimensionality reduction algorithms: (1) None, (2) PCA and (3) K-PCA with RBF kernel.
We perform 10-fold cross-validation on all datasets, for each learning approach, with a training/testing ratio of $60 \%$. To evaluate performance, we take the square root of the MSE defined in \eqref{eq:optim_error}, which we refer to as the joint-velocity RMSE.

Performing such cross-validation in our case, is however not trivial, as our $\mathcal{A}(q)$ formulation has several hyper-parameters, namely the dimensionality $\delta$ of our lower-dimensional embedding $\phi(q)$ and the number of local behavior synergies $K$. Moreover, when using K-PCA (with RBF kernel $k(q,q') = \exp(-\frac{||q-q'||^2}{2\sigma^2})$) we must also find the optimal width $\sigma$ in the RBF kernel. Thus, for each fold and each learning approach we find the optimal hyper-parameters $\delta$, $K$ and $\sigma$ (when applicable), as follows:
\textcolor{red}{\begin{enumerate}[leftmargin=*]
\item Explain how optimal $\delta$ is computed for PCA. 
\item Explain how optimal $\delta$ and $\sigma$ are found for K-PCA.
\item Explain how optimal $K$ is computed for GMM.
\end{enumerate}}

%\begin{figure}[t]
%	\centering	
%		\begin{subfigure}[t]{\linewidth}
%		\centering
%			\includegraphics[width=0.5\linewidth]{new-pics/forehand_crop.png}\hspace{5pt}\includegraphics[width=0.43\linewidth]{new-pics/backhand_crop.png}
%					\caption{Tennis Strokes (left) Forehand (right) Backhand.}
%		\end{subfigure}
%		\begin{subfigure}[t]{\linewidth}
%\centering
%	\includegraphics[width=0.45\linewidth]{new-pics/pour-free_crop.png}\hspace{5pt}\includegraphics[width=0.477\linewidth]{new-pics/pour-obst_crop.png}
%						\caption{Pouring Motions (left) without obstacle (right) with obstacle 1.}
%			\end{subfigure}
%			\begin{subfigure}[t]{\linewidth}		
%\centering
%	\includegraphics[width=0.45\linewidth]{new-pics/pour-obst-2_crop.png}\hspace{5pt}\includegraphics[width=0.5\linewidth]{new-pics/footstep.png}
%	\caption{(left) Pouring Motions with obstacle (right) with obstacle 2 (right) Foot-step motion.}
%				\end{subfigure}
%	\caption{Demonstrated Joint-Space Behaviors with Task-Space Targets. \href{https://www.dropbox.com/sh/3vx512oldgbnkq5/AABP5iEqO0oYn7dlE-gvK1kPa?dl=0}{[videos]} \label{fig:behaviors}}
%	\vspace{-10pt}
%\end{figure}
%
%\begin{table*}[!t]
%\scriptsize
%\begin{center}
%\begin{tabular}{cc|cc|cc}
%    \hline
%    \hline
%    \multicolumn{1}{c}{\multirow{4}{*}{Behavior Dataset}} & \multicolumn{1}{c}{\multirow{4}{*}{Dim. Red. Approach}} & \multicolumn{4}{c}{\multirow{2}{*}{Optimal Parameters | Joint Velocity RMSE [$rad/s$]}}
%	\\  
%    & & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $\delta$}} & \multicolumn{1}{c}{\multirow{2}{*}{Optimal $K$}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Train}} & \multicolumn{1}{c}{\multirow{2}{*}{RMSE Test}}	\\ \\ \hline
%            
%    \multicolumn{1}{c}{\multirow{3}{*}{Backhand Stroke}} & None & 7 & 5.1 $\pm$ (2.643) &\textbf{ 0.192 $\pm$ (0.033)} &  \cellcolor{blue!5} 0.728 $\pm$ (0.709)  \\
%    \multicolumn{1}{c}{\multirow{3}{*}{($M=11,M^*T=1223$)}} & PCA & 3.1 $\pm$ (0.316) & 3.5 $\pm$ (0.971) & 0.216 $\pm$ (0.021) & \cellcolor{blue!10} 0.469 $\pm$ (0.164) \\	
%	& K-PCA ($\sigma = 6.238$) & \textbf{3.1 $\pm$ (0.316)} & \textbf{3.1 $\pm$ (0.316)} & 0.219 $\pm$ (0.013) & \cellcolor{blue!15} 0.355 $\pm$ (0.068)   \\
%	\hline
%	
%	\multicolumn{1}{c}{\multirow{3}{*}{Forehand Stroke}} & None & 7 & 5.5 $\pm$ (2.99) & \textbf{ 0.271 $\pm$ (0.038) } & \cellcolor{blue!5} 0.827 $\pm$ (0.697)  \\
%    \multicolumn{1}{c}{\multirow{3}{*}{($M=10,M^*T=1424$)}} & PCA & 4.1 $\pm$ (0.316) & 4.8 $\pm$ (2.347) & 0.276 $\pm$ (0.033)  & \cellcolor{blue!10} 0.589 $\pm$ (0.367) \\	
%		& K-PCA ($\sigma = 5.488$) & \textbf{3.9 $\pm$ (0.316)} & \textbf{3.2 $\pm$ (0.421)} & 0.305 $\pm$ (0.021) & \cellcolor{blue!15} 0.433 $\pm$ (0.104)  \\
%		\hline
%		
%	\multicolumn{1}{c}{\multirow{3}{*}{Pouring - Free}} & None & 7 & \textbf{ 4.1 $\pm$ (1.286)} & 0.163 $\pm$ (0.026) & 7.609 $\pm$ (18.99) \\
%   \multicolumn{1}{c}{\multirow{3}{*}{($M=9,M^*T=1032$)}} & PCA & \textbf{ 2.3 $\pm$ (0.483)} & 4.8 $\pm$ (2.044) & \textbf{ 0.161 $\pm$ (0.034) } & \cellcolor{blue!10} 0.623 $\pm$ (0.301) \\	
%	& K-PCA ($\sigma = 3.92$) & 3 & 4.3 $\pm$ (1.767) & 0.171 $\pm$ (0.106) & \cellcolor{blue!15} 0.511 $\pm$ (0.305)   \\
%				\hline
%	\multicolumn{1}{c}{\multirow{3}{*}{Pouring - Obstacle}} & None & 7 & 6.2 $\pm$ (2.573) & \textbf{0.247 $\pm$ (0.039)} & 3.049 $\pm$ (3.113) \\
%   \multicolumn{1}{c}{\multirow{3}{*}{($M=11,M^*T=1232$)}} & PCA & 3.8 $\pm$ (0.421) & 3.8 $\pm$ (1.549) & 0.292 $\pm$ (0.018) & \cellcolor{blue!10} 0.486 $\pm$ (0.125) \\	
%				& K-PCA ($\sigma = 7.695$) & \textbf{ 3.1 $\pm$ (0.421) } & 3.1 $\pm$ (0.316) & 0.288 $\pm$ (0.020) & \cellcolor{blue!15} 0.482 $\pm$ (0.078)   \\
%				\hline	
%	\multicolumn{1}{c}{\multirow{3}{*}{Foot Swing}} & None & 7 & 4.4 $\pm$ (2.366) & \textbf{ 0.080 $\pm$ (0.008) } & 0.368 $\pm$ (0.265)  \\
%	\multicolumn{1}{c}{\multirow{3}{*}{($M=8,M^*T=1058$)}} & PCA & \textbf{1} & 3.2 $\pm$ (0.421) & 0.084 $\pm$ (0.004) & \cellcolor{blue!10}  0.123 $\pm$ (0.011) \\	
%	& K-PCA ($\sigma = 1.513$) & 3.2 $\pm$ (0.421) & \textbf{3} &  0.091 $\pm$ (0.007) & \cellcolor{blue!15} 0.115 $\pm$ (0.015)   \\
%				\hline		
%	
%	\multicolumn{1}{c}{\multirow{3}{*}{Singularity Motions}} & None & 7 & 6.2 $\pm$ (2.898) & 0.054 $\pm$ (0.009) & 0.137 $\pm$ (0.098)  \\
%    \multicolumn{1}{c}{\multirow{3}{*}{($M=10,M^*T=1467$)}} & PCA & \textbf{2} & 6 $\pm$ (2.357) & \textbf{ 0.053 $\pm$ (0.010) } & \cellcolor{blue!10} 0.105 $\pm$ (0.046) \\	
%	& K-PCA ($\sigma = 1.769$) & 3.6 $\pm$ (0.516) & \textbf{5.3 $\pm$ (2.452)} & 0.055 $\pm$ (0.018) & \cellcolor{blue!15} 0.071 $\pm$ (0.010)   \\ \hline\hline
%\end{tabular}
%\caption{\scriptsize Performance Comparison of Learning Approach with different Dimensionality Reduction Schemes. We present the \texttt{mean(std)} for the optimal lower-dimensional $d$ and behavior synergies $K$ and RMSE on training and testing set, found for every learning scheme over 10 runs.\label{tab:learning}}
%\end{center}
%\vspace{-10pt}
%\end{table*}

@@

@@

\begin{table}[t]
	\centering
	\resizebox{\linewidth}{!}{\begin{tabular}{l|c|c|c|c}
		\hline \hline
		& No. Dem. & No. K & $\phi(q)$ dim. & $e_{totol}$ [{rad}/{s}] \\ \hline
		Obstacle avoidance (JT-DS)  &      7                &     4             &        4  &  0.0137    \\ 
		Obstacle avoidance (SEDS) &      7                &     3             &        -  &   -   \\		
		\hline
		Foot step  (JT-DS) &       3               &     1             &          1 & 0.01344   \\ 
		Foot step (SEDS)&       3               &     1             &          - & -   \\ \hline \hline
	\end{tabular}}
	\caption{Parameters and Performance of Comparative Experiments \textcolor{red}{(REDO)} }
	\label{table:1}
\end{table}

\begin{figure}[t]
	\vspace{-0.05cm}
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=0.45\linewidth]{Pic/Luggage1.png}
		\includegraphics[width=0.143\linewidth]{Pic/Luggage2.png}
		\includegraphics[width=0.377\linewidth]{Pic/Luggage3.png}
		\caption{Desired Joint Behavior: obstacle avoidance motion. The luggage is the obstacle.}
		\label{fig:snapshot:a}
	\end{subfigure}\\
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=0.33\linewidth]{Pic/Luggage4_SEDS.png}
		\includegraphics[width=0.33\linewidth]{Pic/Luggage3_SEDS.png}
		\includegraphics[width=0.32\linewidth]{Pic/Luggage3_SEDS.png}
		\caption{Desired Behavior: The Cartesian DS is used to generate the motion.}
		\label{fig:snapshot:b}
	\end{subfigure}\\
	\begin{subfigure}[t]{\linewidth}
		\centering	
		\includegraphics[angle=180,origin=c,width=0.45\linewidth]{Pic/1.png}~~
		\includegraphics[angle=180,origin=c,width=0.45\linewidth]{Pic/3.png}\\\vspace{0.1cm}
		\includegraphics[angle=180,origin=c,width=0.45\linewidth]{Pic/4.png}~~
		\includegraphics[angle=180,origin=c,width=0.45\linewidth]{Pic/2.png}
		\caption{Desired Joint Behavior: Foot step-like motion.}
		\label{fig:snapshot:c}
	\end{subfigure}\\	
	\caption{Snapshots of the robot experiments. A corresponding video is available on-line \href{https://youtu.be/1dgKfmN1UgE}{[video link]}. \textcolor{red}{REDO} }
	\label{fig:snapshot}
	\vspace{-0.8cm}
\end{figure}

@@

\begin{figure}[t]
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{Pic/cropped_Sing_1.pdf}
		\caption{ }
		\label{fig:Sin}
	\end{subfigure}\\
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{Pic/cropped_Sing_2.pdf}
		\caption{ }
		\label{fig:Det}
	\end{subfigure}\\
	\caption{The experiment generated $K=3$ Gaussian components. As the first joint is the only joint which was not fixed during the demonstration, the learned augmentation matrices had only one nonzero entry $A_k(1,1)\neq0~\forall k\in \{1, 2, 3\} $.  In (a), the end-effector positions for the demonstrations and executed motions are plotted in Cartesian space. The JT-DS trajectory was generated closed-loop, while the SEDS trajectory was generated open-loop (otherwise it would be unstable). In (b), the determinants of the Jacobian $(|J(q)J^T(q)|)$ for all $10$ JT-DS motions are superimposed. Due to sensory noise, the determinants are not exactly zero, but are very close.  }
	\vspace{-10pt}
\end{figure}
